### 2018-03-23 Sections/economics_of_the_quantum_internet.tex
Economics figs
Some more economics

@@

@@

@@

@@

>>>>

Examples of the temporal dynamics of the cost of computation are shown in Fig.~\ref{fig:econ_cost_of_comp}.

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=1$}.}\label{fig:econ_cost_of_comp}
\end{figure}

@@

Examples of the temporal dynamics of the time-dependent single-qubit QCL are shown in Fig.~\ref{fig:time_dep_QCL}.

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{single_qubit_QCL}
\caption{Time-dependent quantum computational leverage for a single qubit with different computational scaling functions, under the assumption of exponential network growth with \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{qubit_ass_pricing_model}
\caption{\comment{To do}}\label{fig:qubit_ass_pricing_model}
\end{figure}

\comment{What's the difference between this and the hardware cost???}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod}
\caption{Forward contract price on a single physical qubit to be delivered at time $T$ in the future. Units are \mbox{$C_0=1$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

\comment{Point at which it becomes negative!!}
